Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-27 Chapter-2/2-LArTPCs.tex
s

\subsubsection{Effects Modifying the  Light Yield}
The production mechanism through emission from bound excimer states implies that argon is  transparent to its own scintillation light. In fact, the photons emitted from these metastable states are not energetic enough to re-excite the argon bulk, greatly suppressing absorption mechanisms. In a LArTPC however, several processes modify the light yield in between the location where light is produced and the optical detector. In a hypothetical pure tank of argon, Rayleigh scattering would be the most important processes modifying the light yield. Rayleigh scattering changes the path of light propagation in argon, prolonging the time between light production and detection.  The scattering length has been measured to be 66 cm \textcolor{red}{[191]} , shorter than the theoretical prediction of $\sim$~90 cm \textcolor{red}{[190]}; this value is short enough to be relevant for the current size of LArTPCs detectors. In fact, Rayleigh scattering worsen the resolution on $t_0$, the start time for charge drifting, and  alters the light directionality, complicating the matching between light and charge coming from the same object in case of multiple charged particles in the detector.

@@

The stringent constraints for the electron life time limit the presence of oxygen and water to such a low level that both absorption and quenching on these impurity is not expected to be significant \textcolor{red}{[210]}.   Contrarily, the nitrogen level is not bound by the electron life time constraints -- nitrogen being an inert gas, expensive to filter. Thus, nitrogen is often present at the level provided by the vendor. The effects of nitrogen on argon scintillation light have been studied in the WArP R\&D program and at several test stands.
The quenching process induced by nitrogen in liquid Ar has been measured to be proportional to the nitrogen concentration, with a rate constant of $\sim  0.11$ $\mu s^{-1}$ ppm$^{-1}$; appreciable decreasing in lifetime and relative amplitude of the slow component have been shown for contamination as high as a few ppm of nitrogen \cite{1748-0221-5-06-P06003}.
For a nitrogen  concentration of 2 parts per million,  typical of the current generation of LArTPC, the attenuation length due to nitrogen has been measured to be $\sim$30 meters \cite{1748-0221-8-07-P07011}.

\subsubsection{Wavelength Shifting of LAr Scintillation Light}
Liquid argon scintillation light is invisible for most optical detectors deployed in LArTPC, such as cryogenic PMTs and SiPMs, since a wavelength of 128 nm is  generally too short to be absorbed from most in glasses, polymers and semiconductor materials. Research on prototype SiPMs absorbing directly VUV light and their deployment in noble gasses experiment is ongoing but not mature \cite{1748-0221-8-01-C01003}. Thus, experiments need to shift the wavelength of scintillation light to be able to detect it.  Albeit deployed in different ways, neutrinos and dark matter experiments commonly use  1,1,4,4-tetraphenyl-butadiene (TPB) to shift the scintillation light. 
TPB, whose chemical structure is shown in figure , absorbs the vacuum ultraviolet (VUV) light and emits in the visible at $\sim$~425 nm \textcolor{red}{[231]}, with a ratio of visible photon emitted per VUV photon absorbed of $\sim$1.2:1 \cite{GEHMAN2011116}.

Neutrino experiments typically coat their optical detector system evaporating a layer of TPB either directly on the PMTs glass surface or on acrylic plates mounted in front of the PMTs \textcolor{red}{cite microboone}; this technique allows the fast detection light coming directly from the neutrino interaction. Dark matter experiments typically evaporate TPB on reflective foils mounted on the inside walls of the sensitive volume and detect the light after it has been reflected; this technique leads to a higher and more uniform light yield, though scattering effects for both the visible and VUV light augment the propagation time and hinder directionality information\textcolor{red}{some DM detector} . In order to take advantage of both these techniques, hybrid systems with PMT coating and foils are being considered for the next generation of large neutrino detectors \textcolor{red}{cite SBND?}.

>>>>

\subsubsection{Effects Modifying the  Light Yield}
The production mechanism through emission from bound excimer states implies that argon is  transparent to its own scintillation light. In fact, the photons emitted from these metastable states are not energetic enough to re-excite the argon bulk, greatly suppressing absorption mechanisms. In a LArTPC however, several processes modify the light yield in between the location where light is produced and the optical detector. In a hypothetical pure tank of argon, Rayleigh scattering would be the most important processes modifying the light yield. Rayleigh scattering changes the path of light propagation in argon, prolonging the time between light production and detection.  The scattering length has been measured to be 66 cm \cite{Ishida1997} , shorter than the theoretical prediction of $\sim$~90 cm \cite{Teague1968}; this value is short enough to be relevant for the current size of LArTPCs detectors. In fact, Rayleigh scattering worsen the resolution on $t_0$, the start time for charge drifting, and  alters the light directionality, complicating the matching between light and charge coming from the same object in case of multiple charged particles in the detector.

@@

The stringent constraints for the electron life time limit the presence of oxygen and water to such a low level that both absorption and quenching on these impurity is not expected to be significant.   Contrarily, the nitrogen level is not bound by the electron life time constraints -- nitrogen being an inert gas, expensive to filter. Thus, nitrogen is often present at the level provided by the vendor. The effects of nitrogen on argon scintillation light have been studied in the WArP R\&D program and at several test stands.
The quenching process induced by nitrogen in liquid Ar has been measured to be proportional to the nitrogen concentration, with a rate constant of $\sim  0.11$ $\mu s^{-1}$ ppm$^{-1}$; appreciable decreasing in lifetime and relative amplitude of the slow component have been shown for contamination as high as a few ppm of nitrogen \cite{1748-0221-5-06-P06003}.
For a nitrogen  concentration of 2 parts per million,  typical of the current generation of LArTPC, the attenuation length due to nitrogen has been measured to be $\sim$30 meters \cite{1748-0221-8-07-P07011}.

\subsubsection{Wavelength Shifting of LAr Scintillation Light}
Liquid argon scintillation light is invisible for most optical detectors deployed in a LArTPC, such as cryogenic PMTs and SiPMs, since a wavelength of 128 nm is  generally too short to be absorbed from most in glasses, polymers and semiconductor materials. Research on prototype SiPMs absorbing directly VUV light and their deployment in noble gasses experiment is ongoing but not mature \cite{1748-0221-8-01-C01003}. Thus, experiments need to shift the wavelength of scintillation light to be able to detect it.  Albeit deployed in different ways, neutrinos and dark matter experiments commonly use  1,1,4,4-tetraphenyl-butadiene (TPB) to shift the scintillation light. 
TPB  absorbs the vacuum ultraviolet (VUV) light and emits in the visible at $\sim$~425 nm \cite{Burton1973}, with a ratio of visible photon emitted per VUV photon absorbed of $\sim$1.2:1 \cite{GEHMAN2011116}.

Neutrino experiments typically coat their optical detector system evaporating a layer of TPB either directly on the PMTs glass surface or on acrylic plates mounted in front of the PMTs \cite{Acciarri2017}; this technique allows the fast detection light coming directly from the neutrino interaction. Dark matter experiments typically evaporate TPB on reflective foils mounted on the inside walls of the sensitive volume and detect the light after it has been reflected; this technique leads to a higher and more uniform light yield, though scattering effects for both the visible and VUV light augment the propagation time and hinder directionality information\cite{Aalseth2018}. In order to take advantage of both these techniques, hybrid systems with PMT coating and foils are being considered for the next generation of large neutrino detectors.
